---
title: "Activity 2.7 - Exploratory Data Analysis: Taking Control of Your Factors"
author: "INSERT TEAM NAME HERE"
date: "INSERT TODAY'S DATE HERE"
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(gapminder)
```


### Exercise 1

```{r}
str(gapminder$continent)
levels(gapminder$continent)
nlevels(gapminder$continent)
class(gapminder$continent)
```

The str function returns each different level of continent as a string, then prints the number it is stored as arbitrarily in R. For example, all rows with 'Africa' as its continent have a 3 stored as the value for continent in R.
The levels function returns the value for each level of continent as a string. The default ordering of each level seems to be alphabetically. In this case, this makes sense because continent is not ordinal so the order they appear does not matter.
The nlevels function returns a count of the unique values for continent.
The class function returns the type of variable continent is. Continent is a factor (categorical), rather than an integer/numerical.


### Exercise 2

```{r two}
fct_count(gapminder$continent)
```

### Exercise 3

```{r three}
h_countries <- c("Egypt", "Haiti", "Romania", "Thailand", "Venezuela")
h_gap <- gapminder %>%
  filter(country %in% h_countries)
nlevels(h_gap$country)
h_gap_droplevels <- h_gap %>% 
  droplevels()
nlevels(h_gap_droplevels$country)
```
The levels in h_gap still appear to be 142, but it should by 5.

### Exercise 4

...


### Exercise 5

...


### Exercise 6

...



### Exercise 7

...

